MSHS COVID-19 Vaccinations

### 2021-03-30 Evening-Huddle-Stats.Rmd
Continue working on saving and importing data for Tableau.

```{r Create and combine tables with vaccine administration and schedule data}
# Summarize total doses to date through today -------------
admin_to_date <- daily_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, Dose) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

@@

# Summarize scheduled data for the next 7 days ---------------
next_7days_sched <- daily_sched_summary %>%
  filter(ApptDate %in% seq(from = today + 1, to = today + 7, by = 1)) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(SchedVisits = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = ApptDate,
              values_from = SchedVisits,
              names_sort = TRUE)

# Create a template of all sites, vaccine dates, and doses ---------
site_rep <- data.frame("Site" = sort(rep(all_sites,
                                         length(doses))))

>>>>

```{r Create and combine tables with vaccine administration and schedule data}
# Create a template of all sites, vaccine dates, and doses ---------
site_rep <- data.frame("Site" = sort(rep(all_sites,
                                         length(doses))))

# Create template of next 7 days for each site and dose to ensure holidays are included
next_7days <- seq(from = today + 1, to = today + 7, by = 1)

next_7days_rep <- data.frame("ApptDate" = rep(next_7days,
                                          length(all_sites)))

site_next_7days_rep <- data.frame("Site" = sort(rep(all_sites,
                                                    length(next_7days))))

site_next_7days_templ <- cbind(site_next_7days_rep, next_7days_rep)

site_dose_next_7days_templ <- left_join(site_dose_rep,
                                        site_next_7days_templ,
                                        by = c("Site" = "Site"))

# Summarize total doses to date through today -------------
admin_to_date <- daily_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, Dose) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

@@

# Summarize scheduled data for the next 7 days ---------------
next_7days_sched <- daily_sched_summary %>%
  filter(ApptDate %in% next_7days) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(SchedVisits = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

next_7days_sched <- left_join(site_dose_next_7days_templ, next_7days_sched,
                              by = c("Site" = "Site",
                                     "Dose" = "Dose",
                                     "ApptDate" = "ApptDate"))

next_7days_sched <- next_7days_sched %>%
  pivot_wider(names_from = ApptDate,
              values_from = SchedVisits,
              names_sort = TRUE)
